Woah cool a proper git paper!

### 2021-11-19 main.Rmd
Fix

---
title: "Woah cool a proper git paper!"
author: "Ryan, Brown, & Platt"
date: `r format(Sys.Date() + lubridate::years(20),"%A, %B %d, %Y")`
output: bookdown::pdf_document2
toc: yes
bibliography: references.bib
csl: aag.csl
---

>>>>

---
title: "Woah cool a proper git paper!"
author: "Ryan, Brown, & Platt"
date: "`r format(Sys.Date() + lubridate::years(20),'%A, %B %d, %Y')`"
output: bookdown::pdf_document2
toc: yes
bibliography: references.bib
csl: aag.csl
---
